Evaluating Open Information Extraction for Ontologization of a Thematic Domain

### 2014-07-18 paper/ekaw-2014/ekaw2014.tex
EKAW 2014 changes done

\medskip
\noindent
\textbf{ReVerb \& OpenIE 4.0:}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb~\cite{Fader2011a} and OpenIE 4.0~\cite{Mausam2012a}, which are shown to have outperformed the earlier systems such as TextRunner~\cite{Etzioni2008a}, $woe^{pos}$ and $woe^{parse}$~\cite{Wu2010a}. ReVerb addresses the issue of incoherent and uninformative extractions\footnote{We have used the terms \textit{assertions} and \textit{extractions} analogously.} found with the former systems, by using few syntactic and lexical constraints. OLLIE~\cite{Mausam2012a} is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions using semantic role labeling, also known as shallow semantic parsing. The implementations for both ReVerb and OpenIE 4.0 are available online\footnote{Available at https://github.com/knowitall/}.

\medskip
\noindent
\textbf{Semantic parsing:}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It is used in applications such as question-answering systems, robotic navigation and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable~\cite{Harrington2007}. To our knowledge, there is no existing literature that compares semantic parsing with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser and compare with the selected OIE systems. What follows is a brief description of this system.

@@

\medskip
\noindent
\textbf{Text corpus:} Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Pages from the parent categories corresponding to both music traditions are obtained recursively. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to reduce the number of malformed and highly complex sentences. In the semantic parsing based system, to address the multiword named entities, we identify consecutive NNPs and merge them into one in a pre-processing step. In ReVerb and OpenIE4.0, they are handled in their respective implementations.

@@

\medskip
\noindent
\textbf{Gold standard:} We use the ontologies manually engineered with the help of domain experts (one musicologist and three musicians) as groundtruth for the evaluation in the tasks of concept identification and semantic relation extraction\footnote{Available at https://github.com/gopalkoduri/ontologies}. The concepts and relation-types used in our evaluation framework belong to the top most level in the ontologies and are agreed upon by all the experts. The groundtruth for entities for each concept correspond to the page-titles in the respective subcategory in the Wikipedia (eg: Carnatic\_musicians).

@@

\section{Results and discussion}
\label{sec:results}
\subsection{Quantitative assessment}
Figs.~\ref{fig:quant-carnatic-sentences} and \ref{fig:quant-hindustani-sentences} show the distribution of the number of extracted assertions using each of the OIE systems, for sentences in Carnatic and Hindustani music, respectively. Notice that the y-axis is a log scale. Between ReVerb and OpenIE 4.0, the latter seem to perform better, which can be attributed to the noun mediated relations. The semantic parsing based system, however, retrieves substantially more relations per sentence than these two. A tight coupling between syntax and semantics proves to be advantageous in chunking different types of assertions, as well as relating entities far off each other in a given sentence. For instance, in sentences which feature a single subject, but multiple relations (e.g: Chittibabu is a renowned Veena player, born in Kakinada to Ranga Rao and Sundaramma.), it performed thoroughly well compared to others. The difference between their performances for Carnatic and Hindustani music is negligible, which shows that this result is consistent.

Figs.~\ref{fig:quant-carnatic-object} and \ref{fig:quant-hindustani-object} show the corresponding distribution for entities. Recall that we defined an entity to be the subject of a triple. The few entities with a disproportionately high number of extractions are usually the pronouns (despite resolving most of them), followed by musical terms. The semantic parsing based system retrieves slightly more number of assertions per entity compared to OpenIE 4.0, which in turn performs better than ReVerb. We observed some redundancy in assertions for a given entity, which is beneficial as this can be used as a measure of confidence in asserting the corresponding relation. In order to analyze this, we have also plotted the distributions of number of unique extractions for entities (shown in dashed lines in the figures). For Carnatic music, we can observe that the semantic parsing based system retrieves substantially more number of redundant assertions per entity compared to the other two. This difference, however, is less obvious in the case Hindustani music.

Figs.~\ref{fig:quant-carnatic-reltype} and \ref{fig:quant-hindustani-reltype} show the distribution of the number of extracted assertions for the relation types. The results for semantic parsing based system and OpenIE 4.0 are more or less the same, both of which are substantially better than ReVerb. The redundancy in assertions, seen as the difference between the distributions shown by solid and dashed lines, is not as pronounced as it is for entities. The decline in the total number of relation-types as the number of extractions go higher, is less steep than in the case of entities. Unless the vocabulary in the domain is itself limited, this may indicate a slightly better coverage of relation types compared to that of the entities in the domain.

Figs.~\ref{fig:quant-carnatic-concept} and \ref{fig:quant-hindustani-concept} show the distribution of the number of extracted assertions for the concepts. Recall that a concept is defined to be the object of a triple with subsumption relation phrase. The difference between the semantic parsing based system and the other two is quite marked, both for Carnatic and Hindustani music, with the former retrieving more assertions per concept. For Hindustani music, the coverage of concepts in the assertions of ReVerb and OpenIE 4.0 is very low, with no concept having more than 20 assertions.

@@

\medskip
\noindent
\textbf{Concept identification.}
Recall that we define candidate concepts to be the collection of objects from the triples with subsumption relation type. We map these to the concepts in the ontologies as described in sec.~\ref{sec:framework}. Table.~\ref{tab:concept_identification} shows the number of concepts in the ontolgies for each music, and the number of concepts mapped from the assertions of the OIE systems. These results are consistent with our earlier observations of the results shown in figs.~\ref{fig:quant-carnatic-concept} and~\ref{fig:quant-hindustani-concept}.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Ontology} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 53 & 4 & 4 & 22 \\
  Hindustani  & 55 & 1 & 2 & 9 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of concepts in the ontologies for each music, and those mapped from the assertions of the OIE systems.}
\label{tab:concept_identification}
\end{table}

@@

In most categories and for all the three systems, it can be seen that $R$ grows quickly over iterations, making the residual portion the majority among the candidate entities, which brings the precision down. The semantic parsing based system consistently outperforms the other two methods, both in terms of having higher $O$, and lower $R$. Between ReVerb and OpenIE 4.0, there is no substantial difference in terms of $O$. For Carnatic singer and instrumentalist categories, however, the latter results in a lower $R$, and a slightly higher $O$ compared to the former. These results partly contrast with those obtained for the rule-based concept assignment (fig.~\ref{fig:qual-object-rulebased}). However, remember that the coverage of concepts in the domain is observed to be remarkably better in the case of the semantic parsing based system 
(figs.~\ref{fig:quant-carnatic-concept} and~\ref{fig:quant-hindustani-concept}). As the bootstrapping method uses the objects from the triples (which are the candidate concepts), it seems logical that the semantic parsing based system has performed substantially better than the other two.

@@

In terms of the breadth of the valid relation types (see sec.~\ref{sec:framework}), the semantic parsing based system performs better than OpenIE 4.0, which in most cases fares better than ReVerb. However, in terms of the depth of relation types, both the semantic parsing based system and OpenIE 4.0 perform competitively, with the former scoring high in a few categories while the latter in few others. Compared to these two, ReVerb scores substantially less in this task. This can be attributed to two reasons: the former two handle noun-mediated relations, whereas ReVerb does not, the average number of assertions for a noun-mediated relation type is observed to be usually higher than the verb-mediated relations. The second reason can be specific to the domain, where the relations with musical concepts are mostly noun-mediated (e.g: Abhogi, is a raga in, Carnatic music). Notice that there is a strong concurrence between these results and those shown in figs.~\ref{fig:quant-carnatic-reltype} and \ref{fig:quant-hindustani-reltype}, with a noticeable correlation in the differences between the performance of the OIE systems.

>>>>

\medskip
\noindent
\textbf{ReVerb \& OpenIE 4.0}
For demonstrating our evaluation framework, we choose two state-of-the-art OIE systems: ReVerb~\cite{Fader2011a} and OpenIE 4.0~\cite{Mausam2012a}, which are shown to have outperformed the earlier systems such as TextRunner~\cite{Etzioni2008a}, $woe^{pos}$ and $woe^{parse}$~\cite{Wu2010a}. ReVerb addresses the issue of incoherent and uninformative extractions\footnote{We have used the terms \textit{assertions} and \textit{extractions} analogously.} found with the former systems, by using few syntactic and lexical constraints. OLLIE~\cite{Mausam2012a} is a successor of ReVerb, and includes the noun-mediated relations which are not handled by the latter. It also incorporates the context of the assertions in the form n-ary relations. OpenIE 4.0 employs a similar methodology to that of OLLIE, to retrieve assertions using semantic role labeling, also known as shallow semantic parsing. The implementations for both ReVerb and OpenIE 4.0 are available online\footnote{Available at https://github.com/knowitall/}.

\medskip
\noindent
\textbf{Semantic parsing}
On the other hand, deep semantic parsing is an active research topic in the natural language processing (NLP) community, which aims to obtain a complete logical form of a given sentence. It is used in applications such as question-answering systems, robotic navigation and further has several direct implications for OIE as it is domain-independent and is shown to be web-scalable~\cite{Harrington2007}. To our knowledge, there is no existing literature that compares semantic parsing with the likes of ReVerb and OpenIE 4.0. We therefore built an information extraction wrapper around a state-of-the-art semantic parser and compare with the selected OIE systems. What follows is a brief description of this system.

@@

\medskip
\noindent
\textbf{Text corpus} Our data consists of the plain text obtained from the Wikipedia pages corresponding to the Carnatic and Hindustani music traditions, after removing the tables, listings, figures, infoboxes and other structured content. Pages from the parent categories corresponding to both music traditions are obtained recursively. Text from each page is tokenized to sentences, which are further filtered using the following constraints: a minimum number of 3 words and a maximum of 21 words per sentence, with each word not exceeding 30 characters in length. These constraints are empirically found to reduce the number of malformed and highly complex sentences. In the semantic parsing based system, to address the multiword named entities, we identify consecutive NNPs and merge them into one in a pre-processing step. In ReVerb and OpenIE4.0, they are handled in their respective implementations.

@@

\medskip
\noindent
\textbf{Gold standard} We use the ontologies manually engineered with the help of domain experts (one musicologist and three musicians) as groundtruth for the evaluation in the tasks of concept identification and semantic relation extraction\footnote{Available at https://github.com/gopalkoduri/ontologies}. The concepts and relation-types used in our evaluation framework belong to the top most level in the ontologies and are agreed upon by all the experts. The groundtruth for entities for each concept correspond to the page-titles in the respective subcategory in the Wikipedia (eg: Carnatic\_musicians).

@@

\section{Results and discussion}
\label{sec:results}
\subsection{Quantitative assessment}
The results of quantitative assessment for Carnatic and Hindustani music correlate with each other, which shows that results are consistent\footnote{Due to space constraints, we present results only for Carnatic music. Results for Hindustani music can be found here: https://github.com/gopalkoduri/openie\_eval}. Fig.~\ref{fig:quant-carnatic-sentences} shows the distribution of the number of extracted assertions using each of the OIE systems. Notice that the y-axis is a log scale. Between ReVerb and OpenIE 4.0, the latter seem to perform better, which can be attributed to the noun mediated relations. The semantic parsing based system, however, retrieves substantially more relations per sentence than these two. A tight coupling between syntax and semantics proves to be advantageous in chunking different types of assertions, as well as relating entities far off each other in a given sentence. For instance, in sentences which feature a single subject, but multiple relations (e.g: Chittibabu is a renowned Veena player, born in Kakinada to Ranga Rao and Sundaramma.), it performed thoroughly well compared to others.

Fig.~\ref{fig:quant-carnatic-object} shows the corresponding distribution for entities. Recall that we defined an entity to be the subject of a triple. The few entities with a disproportionately high number of extractions are usually the pronouns (despite resolving most of them), followed by musical terms. The semantic parsing based system retrieves slightly more number of assertions per entity compared to OpenIE 4.0, which in turn performs better than ReVerb. We observed some redundancy in assertions for a given entity, which is beneficial as this can be used as a measure of confidence in asserting the corresponding relation. In order to analyze this, we have also plotted the distributions of number of unique extractions for entities (shown in dashed lines in the figures).We can observe that the semantic parsing based system retrieves substantially more number of redundant assertions per entity compared to the other two.

Fig.~\ref{fig:quant-carnatic-reltype} shows the distribution of the number of extracted assertions for the relation types. The results for semantic parsing based system and OpenIE 4.0 are more or less the same, both of which are substantially better than ReVerb. The redundancy in assertions, seen as the difference between the distributions shown by solid and dashed lines, is not as pronounced as it is for entities. The decline in the total number of relation-types as the number of extractions go higher, is less steep than in the case of entities. Unless the vocabulary in the domain is itself limited, this may indicate a slightly better coverage of relation types compared to that of the entities in the domain.

Fig.~\ref{fig:quant-carnatic-concept} shows the distribution of the number of extracted assertions for the concepts. Recall that a concept is defined to be the object of a triple with subsumption relation phrase. The difference between the semantic parsing based system and the other two is quite marked, with the former retrieving more assertions per concept. For Hindustani music, the coverage of concepts in the assertions of ReVerb and OpenIE 4.0 is very low, with no concept having more than 20 assertions.

@@

\medskip
\noindent
\textbf{Concept identification.}
Recall that we define candidate concepts to be the collection of objects from the triples with subsumption relation type. We map these to the concepts in the ontologies as described in sec.~\ref{sec:framework}. Table.~\ref{tab:concept_identification} shows the number of concepts in the ontolgies for each music, and the number of concepts mapped from the assertions of the OIE systems. These results are consistent with our earlier observations of the results shown in fig.~\ref{fig:quant-carnatic-concept}.
\begin{table}
 \begin{center}
 \begin{tabularx}{0.9\textwidth}{X X X X X}
 \noalign{\hrule height 1.1pt}
  \textbf{Music} & \textbf{\#Ontology} & \textbf{\#ReVerb} & \textbf{\#OpenIE 4.0} & \textbf{\#Sem. Parsing}\\
  \hline
  Carnatic  & 53 & 4 & 4 & 22 \\
  Hindustani  & 55 & 1 & 2 & 9 \\
 \noalign{\hrule height 1.1pt}
 \end{tabularx}
\end{center}
\caption{The number of concepts in the ontologies for each music, and those mapped from the assertions of the OIE systems.}
\label{tab:concept_identification}
\end{table}

@@

In most categories and for all the three systems, it can be seen that $R$ grows quickly over iterations, making the residual portion the majority among the candidate entities, which brings the precision down. The semantic parsing based system consistently outperforms the other two methods, both in terms of having higher $O$, and lower $R$. Between ReVerb and OpenIE 4.0, there is no substantial difference in terms of $O$. For Carnatic singer and instrumentalist categories, however, the latter results in a lower $R$, and a slightly higher $O$ compared to the former. These results partly contrast with those obtained for the rule-based concept assignment (fig.~\ref{fig:qual-object-rulebased}). However, remember that the coverage of concepts in the domain is observed to be remarkably better in the case of the semantic parsing based system 
(fig.~\ref{fig:quant-carnatic-concept}). As the bootstrapping method uses the objects from the triples (which are the candidate concepts), it seems logical that the semantic parsing based system has performed substantially better than the other two.

@@

In terms of the breadth of the valid relation types (see sec.~\ref{sec:framework}), the semantic parsing based system performs better than OpenIE 4.0, which in most cases fares better than ReVerb. However, in terms of the depth of relation types, both the semantic parsing based system and OpenIE 4.0 perform competitively, with the former scoring high in a few categories while the latter in few others. Compared to these two, ReVerb scores substantially less in this task. This can be attributed to two reasons: the former two handle noun-mediated relations, whereas ReVerb does not, the average number of assertions for a noun-mediated relation type is observed to be usually higher than the verb-mediated relations. The second reason can be specific to the domain, where the relations with musical concepts are mostly noun-mediated (e.g: Abhogi, is a raga in, Carnatic music). Notice that there is a strong concurrence between these results and those shown in fig.~\ref{fig:quant-carnatic-reltype}, with a noticeable correlation in the differences between the performance of the OIE systems.
